Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-22 DGMM2025/paper.tex

\usepackage{changes}
\usepackage{amstex}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., [p, q] \subseteq \text{Star}(K)\).
    \end{definition}

>>>>

\usepackage{changes}
%\usepackage{amstex}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\).
    \end{definition}
